%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Ata Altyyev} \\ \vspace{1pt}
    \small 209-446-7533 $|$ \href{mailto:altyew44@gmail.com}{\underline{altyew44@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ataha322}{\underline{linkedin.com/in/ataha322}} $|$
    \href{https://github.com/ataha322}{\underline{github.com/ataha322}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, San Diego}{La Jolla, CA, 9500 Gilman Dr}
      {Bachelor of Science, Mathematics and Computer Science}{Expected January 2024}
          \resumeItemListStart
            \resumeItem{\textbf{Relevant Coursework}}:\\
            Intro Object-Oriented Programming (Java), Advanced Data Structures, Algorithms, Systems Programming (ARMv8 Assembly), Components and Digital Systems (RTL design, boolean logic), Theory of Computations (Finite Automatons and Turing Machines), Discrete Mathematics, Abstract Algebra, Combinatorics, Software Tools, Relativity and Quantum Mechanics.
            
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
% \section{Experience}
%   \resumeSubHeadingListStart

%     \resumeSubheading
%       {Role 1}{November 2021 – Present}
%       {Company 1}{Melbourne, VIC}
%       \resumeItemListStart
%         \resumeItem{Job description/Award/Achievement 1}
%         \resumeItem{Job description/Award/Achievement 2}
%         \resumeItem{Job description/Award/Achievement 3}
%       \resumeItemListEnd
      
%     \resumeSubheading
%       {Role 2}{November 2021 – Present}
%       {Company 2}{Melbourne, VIC}
%       \resumeItemListStart
%         \resumeItem{Job description/Award/Achievement 1}
%         \resumeItem{Job description/Award/Achievement 2}
%         \resumeItem{Job description/Award/Achievement 3}
%       \resumeItemListEnd
      
     
%     \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart

    \resumeProjectHeading
          {\textbf{Planner.xyi} $|$ \emph{Web-application}}{June 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Planner/Calendar/Notepad application. Initially implemented as a web app but will be ported on android. The structure is simple: User-Task interaction. Task modules communicate with user modules through binded UserId's, which allows to store multiple users with their private tasks. Features implemented: registration, login, sort and search, deadline counting, email verification, authentication.}
            \resumeItem{Wrote the backing code with Golang due to the use of the GORM library and use of concurrency with goroutines.}
            \resumeItem{Packaged this program into the docker container for its easy portability.}
            \resumeItem{Stored data in MySQL tables. Cached and encrypted the data with Redis and JWT respectively.}
            \resumeItem{Frontend was implemented with the use of VueJS, Nuxt.js, and Vuetify.}
            \resumeItem{Group Project: backend - \textit{Ata Altyyev}(me), frontend - \href{https://github.com/dzodkin33}{\textit{Boris Ryabov}}.\\
            \url{https://github.com/ataha322/planner.xyi}
            \url{https://github.com/dzodkin33/planner-front}}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Rendering} $|$ \emph{Real time rendered graphics}}{August 2022}
          
          \resumeItemListStart
            \resumeItem{Real time rendered graphics using C++, SFML, OpenGL.}
            \resumeItem{This is a part of my learning of OpenGL, guided project. Implemented a moving camera, randomly generated buildings, fog, built a texture cube.}
            \resumeItem{Technical significancies lied in bitwise operations and geometry calculations.}
          \resumeItemListEnd
          
    \resumeProjectHeading
          {\textbf{Newton's box} $|$ \emph{2D Gravity simulation}}{July 2022}
          \resumeItemListStart
            \resumeItem{2D planet gravity simulation. Moon rotates around its planet where planet is a movable object to demostrate changes in inertial and accelerated frames.}
            \resumeItem{Used C++ and SFML library to implement two key objects: planet and its moon. Gravity calculations are made in the moon object, with planet object passed in. Planet is movable, simulation is resettable, window frames are adjoint.}
            \resumeItem{Technical details: $F = G \dfrac{m_1m_2}{d^2}$}
            \resumeItem{\url{https://github.com/ataha322/newtonBox}}
          \resumeItemListEnd
          
    \resumeProjectHeading
          {\textbf{HackMerced V} $|$ \emph{Hackathon project}}{February 2020}
          \resumeItemListStart
            \resumeItem{Gym app for Android. App was supposed to recognize gym equipment and display the corresponding exercise from YouTube. My work: open the gallery, import the selected image, display on the main menu; feed 300 images of basic gym equipment to ML Kit.}
            \resumeItem{Technologies used: Kotlin, Android Studio, ML Kit.}
            \resumeItem{Accomplished: Main menu and picture selection worked out. Image recognition worked on the gym equipment.}
            \resumeItem{\url{https://devpost.com/software/myexercise}}
          \resumeItemListEnd
          

    \resumeSubHeadingListEnd



%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Golang, Java, Python, Pascal, ARM Assembly, TypeScript} \\
     \textbf{Libraries \& Frameworks}{: Docker, Redis, Gorm(MySQL), Fiber, JWT, Stripe, VueJS, Nuxt.js, Vuetify, SFML, Faker} \\
     \textbf{Developer Tools}{: GDB, Valgrind, Linux, Git, bash \& make scripts, RaspberryPi (C-code, ARM-code), \LaTeX} \\
     \textbf{Side Skills}{: ASM reverse engineering, Golang TDD, Matlab} \\
     \textbf{Miscellaneous}{: Burnt serial programmer by connecting two power sources, \href{https://github.com/ataha322/dvd-bounce}{{\underline{DVD-like bouncing screensaver}}}}
    }}
 \end{itemize}
 


%-------------------------------------------
\end{document}
